\textbf{Integrating spatial and temporal patterns \\ in ecological forecasts }

### 2018-07-03 doc/manuscript.tex
Finished writing up community example

\author[1]{Peter B. Adler}  %\thanks{Corresponding author. Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah Email: peter.adler@usu.edu}}
\author[2]{Ethan White}
\author[3]{Michael Cortez?}
\author[4]{others?}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{some shitty Florida joint}

@@

In the previous example, evolutionary change was the slow process whose rate determined the shift in weight from the temporal to spatial forecast of the state of a population. The process of compositional turnover--change in the abundances and identities of species interacting at a site--can have a similar effect at the community level. We demonstrate this using a metacommunity model developed by Alexander et al. (ref). The model describes Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of offspring of each species leaves the site where they were produced and reaches all other sites with equal probability.

@@

The temporal model, which we call $T$, starts with a time series of ``observed" population sizes, $\vec{N}$. Using data from a baseline period with a stationary distribution of annual temperature at one location, we fit the following regression, which predicts the (log) population growth rate as a function of population size and annual temperature at time $t$:
 \begin{equation}
 \ln(\frac{N_{t+1}}{N_t}) = T(N_t,K_t) = \beta^T_0 +  \beta^S_1 ln(N_t) +\beta^S_2 K_t + beta^S_3 {K_t}^2 +  \varepsilon
 \label{eqn:temporal_regression}
 \end{equation}

@@

-Describe spatial model

-Describe temporal model

-Model weights

>>>>

\author[1]{Peter B. Adler}  %\thanks{Corresponding author. Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah Email: peter.adler@usu.edu}}
\author[2]{Ethan White}
\author[1]{Michael Cortez?}
\author[3]{Heather Lynch?}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{some shitty Florida joint}

@@

In the previous example, evolutionary change was the slow process that determined how quickly the combined model shifted from a temporal to spatial forecast. The process of compositional turnover--change in the abundances and identities of species interacting at a site--can have a similar effect at the community level. We demonstrate this using a metacommunity model developed by Alexander et al. (ref). The model describes Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of offspring of each species leaves the site where they were produced and reaches all other sites with equal probability.

@@

The temporal model, which we call $T$, starts with a time series of ``observed" population sizes, $\vec{N}$. Using data from a baseline period with a stationary distribution of annual temperature at one location, we fit the following regression, which predicts the (log) population growth rate as a function of population size and annual temperature at time $t$:
 \begin{equation}
 \ln(\frac{N_{t+1}}{N_t}) = T(N_t,K_t) = \beta^T_0 +  \beta^T_1 ln(N_t) +\beta^T_2 K_t + beta^T_3 {K_t}^2 +  \varepsilon
 \label{eqn:temporal_regression}
 \end{equation}

@@

The spatial model for total community biomass is a simple linear regression. The spatial model for the biomass of the focal species is a multiple regression with a quadratic term, identical to Eqn. \ref{eqn:spatial_regression}. The temporal model for total biomass, $M$, is:
 \begin{equation}
 \ln(M_{t+1} = T(M_{t},K_t) = \beta^T_0 +  \beta^T_1 M_t +\beta^T_2 K_t  +  \varepsilon .
 \label{eqn:community_temporal_regression}
 \end{equation}
The temporal model for focal species biomass has the same functional form. The combined models are based on the same approach that we used in the eco-evolutionary example (eqn. \ref{eqn:combined_model}).
